Incentivizing Exploration by Heterogeneous Users

### 2018-02-16 algorithm.tex
significant reorg of Section 4

To capture the probability masses of problematic agents,
we define
$\AlmostTied{\delta} = \Prob[\AgV \sim \AgentDist]{%
\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \delta}$
to be the total probability mass (across all arms) of agents
whose (actual) preference for their best arm over their second-best
arm is at most $\delta$.
\pfcomment{We can check through the whole paper on whether we write
$\AgV \sim \AgentDist$, $\AgentDist$ or $\AgV$ in the subscript, and make the use consistent.
  Here we write $\AgV \sim \AgentDist$ while we have only $\AgentDist$ in the definition of $p$ in the problem description.}
%The minimum probability mass of users who prefer their best arm
%sufficiently strongly over their second-best arm is denoted by
%$\ClearPref{\delta} = \min_{i}
%\Prob[\AgV \sim \AgentDist]{\Best{\AgV}=i,%
%\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) > \delta}$.
%Notice that \AlmostTied{\delta} (being a measure of problematic
%agents) is defined as a sum over all arms,
%while  \ClearPref{\delta} (being a measure of non-problematic agents)
%is defined as a minimum over arms.
%Also notice that $\ClearPref{0} = \MinProb$.
\dkcomment{We should stress somewhere that we assume that actual ties
  have measure 0.}

In this section, we prove that Algorithm~\ref{alg:basic-incentivizing} achieves $O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) +
O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3)$ cumulative regret with $O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right)$ payment budget.  This is stated in the following pair of theorems, which together constitute our main results.

\dkcomment{Depending on how we structure Section 3, we might
get rid of those theorems, and only consider them parts of Theorem 2
that we prove here.}
% We now prove our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret}.

@@

@@

The key technical lemma captures the intuition that
the estimates of the arms' attribute vectors become
more accurate with increasing phases $s$.
That intuition is captured by the following lemma.

\begin{lemma} \label{lem:round-prob}
Let $x > 0$ be arbitrary.
Recall that $\sigma$ is the standard deviation of the Gaussian noise.
Let $\LatePhase \geq \max (2, \frac{30 \sigma^3}{x^3})$.
Let $\History{t}$ denote the random vector
$(\Pull{1}, \ldots, \Pull{t}, \PayA{1}, \ldots, \PayA{t}, \ObsV{1}, \ldots, \ObsV{t})$
and let $\tau$ be a stopping time 
with respect to the filtration generated by $(\History{t} : t \ge 0)$.
Assume that $\tau$ is almost surely in phase $s$,
i.e., satisfying $\tau \in [t_s, t_{s+1})$ almost surely.
Then, for all phases $s \geq \LatePhase$,
with (unconditional) probability at least 
$1- 24 \ARMNUM d \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$,
the following holds for all arms $i$ and attributes $j$
simultaneously:
$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq x$.
\dkcomment{We should clarify what the probability is over. It seems to
  be over the entire past history, but not the current type.}
\pfcomment{This is over the entire history, including the current type.  I tried to clarify, but maybe it needs more editing.}
\end{lemma}

@@

\begin{extraproof}{Lemma~\ref{lem:round-prob}}
Fix an arm $i$ and attribute $j$.
By the assumptions of the lemma,
the stopping time $\tau$ is such that almost surely, each arm --- and
in particular arm $i$ --- has been pulled at least
$s \geq \LatePhase$ times at time $\tau$.
Define $J$ to be the number of times that $i$ has been pulled at
time $\tau$.
For any $n \geq 1$, let $k_n$ be the time step right after arm $i$ has
been pulled for the \Kth{n} time. Define
$S_n := \frac{n \cdot (\ArmE{k_n}{i}{j} - \Arm{i}{j})}{2 \sigma}$
to be the sum of all attribute-$j$ noise components up to and
including the \Kth{n} pull of arm $i$, renormalized to have standard deviation $1/2$.
The $S_n$ define an unbiased half-subgaussian random walk,
and we can therefore apply Lemma~\ref{lem:ACI-inequality} to them and
the stopping time $J$.
Specifically, we set $b = \frac{x^2}{16 \sigma^2}$,
and obtain that

\begin{align*}
\Prob{J < \infty \mbox{ and } S_J \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}}
& \leq 12 \exp \left( \frac{-1.8 J x^2}{16 \sigma^2} \right).
\end{align*}

@@

\begin{align*}
\Prob{J < \infty \mbox{ and } |S_J| \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}}
& \leq 24 \exp \left( \frac{-1.8 J x^2}{16 \sigma^2} \right).
\end{align*}

Because $J$ will be finite with probability 1, we can drop the
$J < \infty$ part of the event:
\begin{align*}
& \Prob{S_J \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16
    \sigma^2}}}\\
= & \Prob{J < \infty \mbox{ and } S_J \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16
    \sigma^2}}}.
\end{align*}

In the high-probability case
$|S_J| \leq
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}$,
we first use that $\sqrt{\cdot}$ is sublinear to bound
$\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}
\leq \sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1)} + \frac{J x}{4 \sigma}$
(here we use the fact $\sqrt{J} \leq J$).
Then, we will show momentarily that
$\sqrt{0.6 J \log (\log_{1.1}(J) + 1)} \leq \frac{J x}{4 \sigma}$,
giving us an overall upper bound of
$|S_J| \leq \frac{J x}{2 \sigma}$.

Substituting the definition of $S_J$ and canceling common terms,
the inequality implies that
$|\ArmE{k_J}{i}{j} - \Arm{i}{j}| \leq x$.
The choice of $J$ ensures that
$\ArmE{k_J}{i}{j} = \ArmE{\tau}{i}{j}$,
and we have thus shown that
$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq x$ for all $i,j$.
The lemma now follows by a union bound over all \ARMNUM arms and $d$
attributes.

It remains to show that
$\sqrt{0.6 J \log (\log_{1.1}(J) + 1)} \leq \frac{J x}{4 \sigma}$.
By squaring the statement and rearranging, it is equivalent to show that
$\frac{J}{\log(\log_{1.1}(J)+1)} \geq \frac{9.6\sigma^2}{x^2}$.
Because $J \geq \LatePhase \geq 2$,
a numerical calculation and derivative test shows that
$\frac{J}{\log(\log_{1.1}(J)+1)} \geq J^{2/3}$,
and because $J \geq \LatePhase \geq \frac{30 \sigma^3}{x^3}$,
we get that
$J^{2/3} \geq \frac{9.6 \sigma^2}{x^2}$, completing the proof.
\end{extraproof}

Lemma~\ref{lem:round-prob} implies that the probability of making
large errors due to myopic play decreases exponentially in the phase
number $s$.

\begin{corollary} \label{cor:right-choice}
Let $x > 0$ be arbitrary.
Let $\LatePhase \geq \max (2, \frac{30 \sigma^3}{x^3})$.
Let $\tau$ be a stopping time with respect to the filtration 
generated by $(\History{t} : t \ge 0)$ that is almost surely in phase $s$.
Then, for all $s \geq \LatePhase$,
with (unconditional) probability (over the past history) at least 
$1 - 24 \ARMNUM d \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$,
\dkcomment{We should clarify what the probability is over. It seems to
  be over the past history, but not the current agent.}
\pfcomment{I did the same kind of edits to this corollary as above in Lemma~\ref{lem:round-prob}.  David, can you take a look and resolve or edit?}
an agent of type $\AgV = \AgentV{\tau}$ 
will not pull a highly suboptimal arm, i.e., an arm $i$ with 
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
\end{corollary}

\begin{proof}
Let $\tau$ be a (random) time.
By Lemma~\ref{lem:round-prob},
with probability at least
$1 - 24 \ARMNUM d \cdot \exp \left( \frac{-1.8 s x^2}{16\sigma^2} \right)$,
for all arms $i$ and attributes $j = 1, \ldots, d$ simultaneously,
the estimated attribute $j$ for arm $i$ is close enough to the true attribute: 
$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq x$.
Condition on this high-probability event.

Consider any agent type $\AgV = \AgentV{\tau}$ at the (random) time
$\tau$.
Let $i \neq \Best{\AgV}$ be any arm
with much smaller true reward than the best arm:
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
Because each coordinate of \ArmEV{\tau}{\Best{\AgV}} and of
\ArmEV{\tau}{i} is estimated accurately to within $x$, 
we get that 
$\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
\geq - \Diam d x$
and
$\AgV \cdot (\ArmEV{\tau}{i} - \ArmV{i}) \leq \Diam d x$.
Hence,

\begin{align}
\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmEV{\tau}{i})
& =
\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
+ \AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i})
+ \AgV \cdot (\ArmV{i} - \ArmEV{\tau}{i}) \nonumber\\
& > -\Diam d x + 2 \Diam d x - \Diam d x
\; = \; 0, \label{equ:choice}
\end{align}
which means that the agent with type \AgV will not pull arm $i$
under the high-probability event.
\end{proof}

@@

Towards bounding the algorithm's total payment, we first bound the
\emph{number} of rounds in which the algorithm makes a payment by a
constant.
This bound also turns out to be useful for bounding the total regret.

@@

\begin{proof}
We partition phases into early and late phases.
For each of the early phases,
we crudely bound the number of payments by \ARMNUM,
using that each arm is incentivized at most once per phase.
For later phases,
we use that arms are payment-eligible only if their myopic pulling
probability is less than $1/\log(s)$.
Since at least a \MinProb fraction of agents would prefer arm $i$ if
given accurate estimates, this would require misestimates that make a
significant fraction of agents pull the wrong arm.
But in later phases, such misestimates are unlikely by
Corollary~\ref{cor:right-choice}.

To make this intuition precise, we set
$\delta = \frac{\MinProb}{2 \TieDensity}$,
and $x = \frac{\delta}{2 \Diam d}$.
The cutoff point between early and late phases is now set to
$\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3}, \exp(\frac{2}{\MinProb}))$.
Consider the \Kth{s} pull of an arm $i$, for $s \geq \EvenLaterPhase$.
If this pull occurs before phase $s$, it was definitely not incentivized.
So we condition on the pull occurring in phase $s$,
and let $\tau$ be the time step when this pull occurred; notice that
this means that this must be the first pull of arm $i$ in phase $s$.
We can now apply Corollary~\ref{cor:right-choice}
with this choice of $x$,
and obtain that with probability at least 
$1 - 24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$,
all agent types \AgV with
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}})
> 2\Diam d x = \delta$
will pull their best arm \Best{\AgV}.

By Lemma~\ref{lem:sdelta}, the \emph{total} measure of agents (across
all arms) whose best and second-best arm differ in utility by less
than $\delta$ is at most $\TieDensity \delta = \frac{\MinProb}{2}$.
In particular, this bound holds for agents whose best arm is $i$.
By Assumption~\ref{A3}, at least a measure \MinProb of agents has $i$
as their best arm, and thus, at least a measure $\frac{\MinProb}{2}$
has arm $i$ as their preferred arm by at least $\delta$ over any other
arm $i'$.
In the high-probability event, all such agents would myopically pull
the arm $i$, and as a result, in the high-probability event,
arm $i$ is not payment-eligible.

Thus, for any phase $s \geq \EvenLaterPhase$,
Algorithm~\ref{alg:basic-incentivizing} incentivizes any given arm $i$
with probability at most
$24 \ARMNUM d \cdot \exp \left(
  -\frac{1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
\right)$.
Summing over all arms and phases $s$,
and adding the at most $\ARMNUM \EvenLaterPhase$ incentivizations in
the first \EvenLaterPhase phases, 
the expected total number of arm incentivizations is at most
\begin{align*}
&\ARMNUM \EvenLaterPhase
  + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \nonumber \\
=& O\left( \max\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}, N\exp(\frac{2}{p})\right)
  + \frac{\ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right) \nonumber  \\
=& O\left( N\exp\left(\frac{2}{p}\right) \right).
\end{align*}

@@

It would be desirable to simply identify a constant upper bound on the
payment made each time.
Unfortunately, while the agent types are drawn from a bounded support,
the noise in arm locations is not;
hence, with small probability, arm locations may be grossly
misestimated, resulting in high incentive payments.
As a result, the actual analysis of the total payment is significantly more
intricate, and hence,
the proof of Theorem~\ref{rst:budget} is given in
Appendix~\ref{sec:payment-proof}.

@@

To bound the regret incurred in time steps with large regret,
we use a proof nearly identical to that of
Lemma~\ref{lem:round-prob} and Corollary~\ref{cor:right-choice}.
The only reason we cannot directly apply them is that in order
to apply to arbitrary $x > 0$, we had to assume that
$\LatePhase \geq \frac{30 \sigma^3}{x^3}$, a bound we cannot afford here.
So here, we will choose a larger value of $x$, and in return
will only need to assume that $T \geq 2$.

Let the random variable $t_s$ be the final time step in phase $s$,
for each $s$. Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
time step in the \Kth{s} phase,
with $\tau_{s}^{k} = \infty$ when phase $s$ has fewer than $k$ steps,
i.e., $k > t_{s}-t_{s-1}$.
Exactly as in the proof of Corollary~\ref{cor:right-choice},
it is sufficient to show that with high probability,
$|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq \frac{g(s)}{2\Diam d}$
for all arms $i$ and attributes $j$.

The proof of this high-probability guarantee for the stopping time
$t = \tau_s^k$ is identical to the proof of
Lemma~\ref{lem:round-prob} with $x = \frac{g(s)}{2 \Diam d}$
until the step where we start bounding
$\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}$.
At that point in the proof, we had shown that 
the probability of $|S_J|$ exceeding the preceding expression is at most
\begin{align*}
24 \exp \left( \frac{-1.8 s x^2}{16 \sigma^2} \right)
  & = \frac{24}{T^2}.
\end{align*}

>>>>

Our main result is that Algorithm~\ref{alg:basic-incentivizing} achieves $O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) +
O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3)$ cumulative regret with $O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right)$ payment budget.  This is stated in the following pair of theorems.

\dkcomment{Depending on how we structure Section 3, we might
get rid of those theorems, and only consider them parts of Theorem 2
that we prove here.}

@@

To capture the probability masses of problematic agents,
we define the quantity
$\AlmostTied{\delta} = \Prob[\AgV \sim \AgentDist]{%
\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \delta}$
to be the total probability mass (across all arms) of agents
whose (actual) preference for their best arm over their second-best
arm is at most $\delta$.
\pfcomment{We can check through the whole paper on whether we write
$\AgV \sim \AgentDist$, $\AgentDist$ or $\AgV$ in the subscript, and make the use consistent.
  Here we write $\AgV \sim \AgentDist$ while we have only $\AgentDist$ in the definition of $p$ in the problem description.}
%The minimum probability mass of users who prefer their best arm
%sufficiently strongly over their second-best arm is denoted by
%$\ClearPref{\delta} = \min_{i}
%\Prob[\AgV \sim \AgentDist]{\Best{\AgV}=i,%
%\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) > \delta}$.
%Notice that \AlmostTied{\delta} (being a measure of problematic
%agents) is defined as a sum over all arms,
%while  \ClearPref{\delta} (being a measure of non-problematic agents)
%is defined as a minimum over arms.
%Also notice that $\ClearPref{0} = \MinProb$.
\dkcomment{We should stress somewhere that we assume that actual ties
  have measure 0.}

To formally reason about the event that the estimates of arms'
attributes vectors are accurate enough --- or fail to be so ---
we define the events
$\AccE{t}{i}{j}{\epsilon} := [|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq \epsilon]$
that attribute $j$ of arm $i$ at time $t$ is estimated to
within accuracy $\epsilon$ or better.
Then, 
$\AccEU{t}{\epsilon} = \bigcap_{i,j} \AccE{t}{i}{j}{\epsilon}$
is the event that at time $t$, all arm attribute
estimates are accurate to within $\epsilon$ simultaneously.
We will then show that for suitable choices of $t, x$,
the events \AccE{t}{i}{j}{x}
(and hence, by union bound, \AccEU{t}{\epsilon})
have high probability,
and that when they do, myopic agents do not make large mistakes.

@@

The key technical lemma captures the intuition that
the estimates of the arms' attribute vectors become
more accurate with increasing phases $s$.

\begin{lemma} \label{lem:round-prob}
Recall that $\sigma$ is the standard deviation of the Gaussian noise.
Let \LatePhase be a phase cutoff, 
and let $\epsilon_n, \epsilon'_n > 0$ be functions satisfying that
$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n \epsilon_n^2}{16 \sigma^2}}
\leq \frac{n \epsilon'_n}{2 \sigma}$,
for all $n \geq \LatePhase$.
Let $\tau_s$ be a stopping time
(which may depend on the entire past history)
which is almost surely in phase $s$,
i.e., satisfying $\tau \in [t_s, t_{s+1})$ almost surely.

Then, for any arm $i$, attribute $j$, and phase $s \geq \LatePhase$,
we have that
$\Prob{\AccE{\tau_s}{i}{j}{\epsilon'_s}}
\geq 1 - 24 \exp\left(-\frac{1.8 s \epsilon_s^2}{16 \sigma^2} \right)$.
\end{lemma}

@@

\begin{extraproof}{Lemma~\ref{lem:round-prob}}
Fix an arm $i$ and attribute $j$.
By the assumptions of the lemma,
the stopping time $\tau_s$ is such that almost surely,
each arm --- and in particular arm $i$ --- has been pulled at least
$s \geq \LatePhase$ times at time $\tau_s$.
Define $J$ to be the number of times that $i$ has been pulled at
time $\tau_s$.
For any $n \geq 1$, let $k_n$ be the time step right after arm $i$ has
been pulled for the \Kth{n} time. Define
$S_n := \frac{n \cdot (\ArmE{k_n}{i}{j} - \Arm{i}{j})}{2 \sigma}$
to be the sum of all attribute-$j$ noise components up to and
including the \Kth{n} pull of arm $i$,
renormalized to have standard deviation $1/2$.
The $S_n$ define an unbiased half-subgaussian random walk,
and we can therefore apply Lemma~\ref{lem:ACI-inequality} to them and
the stopping time $J$.
Specifically, we set $b = \frac{\epsilon_J^2}{16 \sigma^2}$,
and obtain that

\begin{align*}
\Prob{J < \infty \mbox{ and } S_J \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J \epsilon_J^2}{16 \sigma^2}}}
& \leq 12 \exp \left( \frac{-1.8 J \epsilon_J^2}{16 \sigma^2} \right).
\end{align*}

@@

\begin{align*}
\Prob{J < \infty \mbox{ and } |S_J| \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J \epsilon_J^2}{16 \sigma^2}}}
& \leq 24 \exp \left( \frac{-1.8 J \epsilon_J^2}{16 \sigma^2} \right).
\end{align*}

Because $J$ will be finite with probability 1, we can drop the
$J < \infty$ part of the event:
\begin{align*}
& \Prob{S_J \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 \epsilon_J^2}{16
    \sigma^2}}}\\
= & \Prob{J < \infty \mbox{ and } S_J \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 \epsilon_J^2}{16
    \sigma^2}}}.
\end{align*}

In the high-probability case, we now apply the assumed inequality
between $\epsilon_J$ and $\epsilon'_J$, to obtain that
\[
|S_J| \; \leq \;
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J \epsilon_J^2}{16 \sigma^2}}
\; \leq \; \frac{J \epsilon'_J}{2 \sigma}.
\]

Substituting the definition of $S_J$ and canceling common terms,
the inequality implies that
$|\ArmE{k_J}{i}{j} - \Arm{i}{j}| \leq \epsilon'_J$.
The choice of $J$ ensures that
$\ArmE{k_J}{i}{j} = \ArmE{\tau_s}{i}{j}$,
and we have thus shown that
$|\ArmE{\tau_s}{i}{j} - \Arm{i}{j}| \leq \epsilon'_s$.
\end{extraproof}

Next, we show the complementary part:
when \AccE{t}{\epsilon} happens, no myopic agent incurs large regret.

\begin{lemma} \label{lem:right-choice}
Let $\epsilon > 0$ be arbitrary.
When \AccEU{t}{\epsilon} happens,
no agent \AgV will pull a highly suboptimal arm, i.e., an arm $i$ with 
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d \epsilon$.
\end{lemma}

\begin{proof}
By definition, when \AccEU{t}{\epsilon} happens,
for all arms $i$ and attributes $j$,
all arm attribute estimates are accurate to within $\epsilon$,
in the sense that
$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq \epsilon$.

Consider any agent type \AgV.
Let $i \neq \Best{\AgV}$ be any arm
with much smaller true reward than the best arm:
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d \epsilon$.
Because each coordinate of \ArmEV{t}{\Best{\AgV}} and of
\ArmEV{t}{i} is estimated accurately to within $\epsilon$, 
we get that 
$\AgV \cdot (\ArmEV{t}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
\geq - \Diam d \epsilon$
and
$\AgV \cdot (\ArmEV{t}{i} - \ArmV{i}) \leq \Diam d \epsilon$.
Hence,

\begin{align}
\AgV \cdot (\ArmEV{t}{\Best{\AgV}} - \ArmEV{t}{i})
& =
\AgV \cdot (\ArmEV{t}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
+ \AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i})
+ \AgV \cdot (\ArmV{i} - \ArmEV{t}{i}) \nonumber\\
& > -\Diam d \epsilon + 2 \Diam d \epsilon - \Diam d \epsilon
\; = \; 0, \label{equ:choice}
\end{align}
which means that the agent with type \AgV will not pull arm $i$.
\end{proof}

@@

As a first step towards bound the total payment (and also regret),
we show that for sufficiently late phases,
under the event \AccEU{t}{\epsilon} for suitably small $\epsilon$,
the algorithm does not offer any payments.

\begin{lemma} \label{lem:no-incentives}
Fix an arm $i$.
Let $s \geq \exp(2/\MinProb)$, and let $\tau_s$ be the (random)
time when arm $i$ is pulled for the \Kth{s} time.
Under \AccEU{\tau_s}{\frac{p}{4\Diam d \TieDensity}},
this pull of arm $i$ is not incentivized.
\end{lemma}

\begin{proof}
By Lemma~\ref{lem:right-choice},
under the event \AccEU{\tau_s}{\frac{\MinProb}{4\Diam d \TieDensity}},
all agent types \AgV with
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}})
> \frac{\MinProb}{2\TieDensity}$
will pull their best arm \Best{\AgV}.

By Lemma~\ref{lem:sdelta}, the measure of agents (across all arms)
whose best and second-best arm differ in utility by less
than $\frac{\MinProb}{2\TieDensity}$ is at most $\frac{\MinProb}{2}$.
In particular, this bound holds for agents whose best arm is $i$.
By Assumption~\ref{A3}, at least a measure \MinProb of agents has $i$
as their best arm, and thus, at least a measure $\frac{\MinProb}{2}$
will myopically pull arm $i$.
Because $1/\log(s) < \frac{\MinProb}{2}$ for
$s \geq \exp(2/\MinProb)$, arm $i$ is not payment-eligible at time
$\tau_s$.
\end{proof}

Towards bounding the algorithm's total payment, we now bound the
\emph{number} of rounds in which the algorithm makes a payment by a
constant.
This bound also turns out to be useful for bounding the total regret.

@@

\begin{proof}
We partition phases into early and late phases.
For each of the early phases,
we crudely bound the number of payments by \ARMNUM,
using that each arm is incentivized at most once per phase.
For later phases,
we use Lemma~\ref{lem:no-incentives},
which rules out any incentives unless large misestimates of the arm
locations occur, which is exponentially unlikely by 
Lemma~\ref{lem:round-prob}.

To make this intuition precise, we set
$\delta = \frac{\MinProb}{2 \TieDensity}$,
and $\epsilon = \epsilon' = \frac{\delta}{2 \Diam d}$
(which is independent of the phase number $s$).
The cutoff point between early and late phases is now set to
$\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{\epsilon^3}, \exp(\frac{2}{\MinProb}))$.
We will verify below that
$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n \epsilon^2}{16 \sigma^2}}
\leq \frac{n \epsilon}{2 \sigma}$
for all $n \geq \max(2, \frac{30 \sigma^3}{\epsilon^3})$.

Fix an arm $i$, and consider the \Kth{s} pull of an arm $i$,
for $s \geq \EvenLaterPhase$.
If this pull occurs before phase $s$, it was definitely not incentivized.
So we condition on the pull occurring in phase $s$,
and let $\tau_s$ be the time step when this pull occurred;
notice that this means that this must be the first pull of arm $i$ in
phase $s$.

By Lemma~\ref{lem:round-prob} (with our choice of $\epsilon = \epsilon'$),
and a union bound over all $i,j$, we bound the probability
$\Prob{\AccEU{\tau_s}{\epsilon}}
\geq 1 - 24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s \epsilon^2}{16 \sigma^2} \right)$.
And by Lemma~\ref{lem:no-incentives},
under the event ${\mathcal E}_{\tau_s}(\epsilon)$,
arm $i$ is not payment-eligible.

Thus, for any $s \geq \EvenLaterPhase$,
the \Kth{s} pull of arm $i$ is incentivized  
with probability at most
$24 \ARMNUM d \cdot \exp \left(
  -\frac{1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
\right)$.
Summing over all arms and phases $s$,
and adding the at most $\ARMNUM \EvenLaterPhase$ incentivizations in
the first \EvenLaterPhase phases, 
the expected total number of arm incentivizations is at most
\begin{align*}
&\ARMNUM \EvenLaterPhase
  + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \nonumber \\
=& O\left( \max\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}, N\exp(\frac{2}{p})\right)
  + \frac{\ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right) \nonumber  \\
=& O\left( N\exp\left(\frac{2}{p}\right) \right).
\end{align*}

It remains to show that
$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n \epsilon^2}{16 \sigma^2}}
\leq \frac{n \epsilon}{2 \sigma}$
for all $n \geq \max(2, \frac{30 \sigma^3}{\epsilon^3}$.
We first use that $\sqrt{\cdot}$ is sublinear to bound
\[
  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n \epsilon^2}{16 \sigma^2}}
\; \leq \; \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1)} + \frac{n \epsilon}{4 \sigma}
\]
(here we use the fact $\sqrt{n} \leq n$).
Next, we show that
$\sqrt{0.6 n \log (\log_{1.1}(n) + 1)} \leq \frac{n \epsilon}{4 \sigma}$;
then, adding the two terms gives the desired bound.

By squaring the claimed statement and rearranging,
it is equivalent to show that
$\frac{n}{\log(\log_{1.1}(n)+1)} \geq \frac{9.6\sigma^2}{\epsilon^2}$.
Because $n \geq 2$,
a numerical calculation and derivative test shows that
$\frac{n}{\log(\log_{1.1}(n)+1)} \geq n^{2/3}$,
and because $n \geq \frac{30 \sigma^3}{\epsilon^3}$,
we get that
$n^{2/3} \geq \frac{9.6 \sigma^2}{\epsilon^2}$, completing the proof.

@@

It would be desirable to simply identify a constant upper bound on the
payment made each time.
Unfortunately, while the agent types are drawn from a bounded support,
the noise in arm locations is not;
hence, with small probability, arm locations may be grossly
misestimated, resulting in high incentive payments.
As a result, the actual analysis of the total payment is significantly more
intricate;
the proof of Theorem~\ref{rst:budget} is given in
Appendix~\ref{sec:payment-proof}.

@@

We next bound the regret incurred in time steps with large regret.
Let the random variable $t_s$ be the final time step in phase $s$,
for each $s$. Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
time step in the \Kth{s} phase,
with $\tau_{s}^{k} = \infty$ when phase $s$ has fewer than $k$ steps,
i.e., $k > t_{s}-t_{s-1}$.
By Lemma~\ref{lem:right-choice},
under \AccEU{\tau_s^k}{\frac{g(s)}{2\Diam d}}, no agent at time $t$ will incur
regret more than $g(s)$.

To bound the probability of \AccEU{\tau_s^k}{\frac{g(s)}{2\Diam d}},
we use Lemma~\ref{lem:round-prob}
(with $\epsilon_s = \epsilon'_s = \frac{g(s)}{2 \Diam d}$
and a stopping time of $\tau_s^k$).
We first verify that this choice of $\epsilon_s, \epsilon'_s$
satisfies the assumption of Lemma~\ref{lem:round-prob} for all
$s \geq 2$,
i.e., that
$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n \epsilon_n^2}{16 \sigma^2}}
\leq \frac{n \epsilon_n}{2 \sigma}$
for all $n \geq 2$.
Substituting that
$\epsilon_n = \frac{g(n)}{2 \Diam d} = \sqrt{\frac{32\log(T) \cdot \sigma^2}{1.8 n}}$,
the left-hand side is

\[
  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{2 \log T}{1.8}}
  \; \leq \;
  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{2 n \log T}{1.8}},
\]
while the right-hand side is $\sqrt{\frac{8 n \log(T)}{1.8}}$.
Squaring both sides and canceling out common terms,
the desired inequality is equivalent to
$\frac{50}{9} \log T \geq \log(\log_{1.1}(n) + 1)$.
Because $n \leq T$, it is sufficient to show that
$\frac{50}{9} \log T \geq \log(\log_{1.1}(n) + 1)$,
which can be verified by numerical calculation for $T=2$ and a
derivative test.

Now, by Lemma~\ref{lem:round-prob} and a union bound over all arms $i$
and attributes $j$, we get that 
\begin{align*}
\Prob{\AccEU{\tau_s^k}{\epsilon_s}}
& \leq 24 \ARMNUM d \cdot \exp \left( \frac{-1.8 s x^2}{16 \sigma^2} \right)
\; = \; \frac{24 \ARMNUM d}{T^2}.
\end{align*}

In the low-probability event, we simply 
bound the maximum regret by \MAXR.
Now, applying Lemma~\ref{lem:phase-length},
the total expected regret from large-regret steps is at most
